Appendix to ``Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis''

### 2016-12-23 MHCpaper/MHCsupp.tex
change of format

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
\documentclass[10pt]{article}
%\usepackage[printfigures]{figcaps}
%\usepackage[nolists,nomarkers]{endfloat}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\hypersetup{colorlinks,linkcolor=blue,citecolor=teal,urlcolor=teal}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figures/"}}
%
\usepackage{array}
%\newcounter{tablerow}[table]
%\newcommand{\tablerowautorefname}{row}
%\newenvironment{tabularn}[1]{\begin{tabular}{#1>{\refstepcounter{tablerow}}l}}{\end{tabular}}
%\usepackage{etoolbox}
%\AtBeginEnvironment{tabular}{\setcounter{tablerow}{0}}
\renewcommand{\figurename}{Appendix-figure}
\renewcommand{\figureautorefname}{Appendix-figure}
\DeclareCaptionLabelFormat{supp}{\textbf{#1 #2}}
\captionsetup{labelformat=supp}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\I}{\mathbf{I}}
%vec of ones
%equilibrium distribution
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%other symbols
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\frg}{\W^\mathrm{F}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
\newcommand{\norm}{_0}
\newcommand{\inc}{_{\text{inc}}}
\newcommand{\dec}{_{\text{dec}}}
\newcommand{\incdec}{_{\text{inc/dec}}}
\newcommand{\wt}{_{\text{WT}}}
\newcommand{\ko}{_{\text{K$^\mathrm{b}$D$^\mathrm{b}$-/-}}}
\newcommand{\KO}{K$^\mathrm{b}$D$^{\mathrm{b}-/-}$}
%\newcommand{\ko}{_{\text{MHC}}}
%\newcommand{\KO}{MHC}
\newcommand{\tpre}{t_{\text{pre}}}
\newcommand{\ttrain}{t_{\text{train}}}
%\newcommand{\lmax}{_{\text{max}}}
%\newcommand{\lmin}{_{\text{min}}}
\newcommand{\modelfig}[1][A]{Figure 4#1 of the main text}
\newcommand{\datafig}[1][B]{Figure 3#1 of the main text}
\newcommand{\chrfig}[1][B]{Figure 2#1 of the main text}
\newcommand{\compfig}[1][A]{Figure 2 -- figure supplement 2#1}
\newcommand{\basefig}{Figure 1 -- figure supplement 2}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Appendix to ``Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis''}
%
%% Author List:
%%
%\author{An Author$^a$, Another Author$^b$ and Yet Another Author$^c$\\
%%
%\small{\emph{$^a$ Address 1}}\\
%\small{\emph{$^b$ Address 2}}\\
%\small{\emph{$^c$ Address 3}}\\
%}
\author{}
\date{}

@@

\begin{figure}
 \begin{center}
   \begin{myenuma}
  \begin{tabular}{l@{\hspace{0.05\linewidth}}l}
    \item\aligntop{\includegraphics[height=1.7cm]{serial.svg}}\label{fig:serial_model}&
    \item\aligntop{\includegraphics[height=1.7cm]{binary.svg}}\label{fig:binary_model}\\[1.7cm]
    \item\aligntop{\includegraphics[height=1.7cm]{multistate.svg}}\label{fig:multistate_model}&
    \item\aligntop{\includegraphics[height=2.5cm]{cascade.svg}}\label{fig:cascade_model}\\[2.5cm]
    \item\aligntop{\includegraphics[height=2.3cm]{pooled_deponly.svg}}\label{fig:pooled_model}&
    \item\aligntop{\includegraphics[height=2.3cm]{multistate_nonuni.svg}}\label{fig:nonuni_model}
  \end{tabular}
   \end{myenuma}
 \end{center}
  \caption[Transition probabilities for different models]{{Transition probabilities for different models.}
  Potentiation induces transitions indicated by orange arrows, depression indicated by blue arrows.
  States of strong/weak synaptic weight indicated by orange/blue circles.
  (\ref{fig:serial_model}) In the serial model the transition probabilities for potentiation/depression are all equal and it is parameterised by these two values.
  The synaptic weight takes only two values, $\pm1$.
  (\ref{fig:binary_model}) The two-state model is parameterised by the two transition probabilities.
  (\ref{fig:multistate_model}) In the multistate model the transition probabilities for potentiation/depression are all equal and it is parameterised  by these two values.
  The synaptic weight varies linearly in the interval $[-1,1]$.
  (\ref{fig:cascade_model}) In the cascade model, the transition probabilities decay geometrically with a parameter $x$ (see \cite{Fusi2005cascade}) and synaptic weight takes only two values.
  (\ref{fig:pooled_model}) In the pooled resource model,
  Several two-state synapses share resources that are required for potentiation and depression.
  These resources are depleted as more synapses are potentiated or depressed.
  This pool of synapses can be modelled as one compound synapse.
  (\ref{fig:nonuni_model}) In the non-uniform multistate model
  the synaptic weight varies linearly in the interval $[-1,1]$, similar to the multistate model, but the transition probabilities between adjacent states decays exponentially away from the central transition for both potentiation and depression.
  } \label{fig:models}
\end{figure}

@@

\begin{figure}[p]
\begin{myenuma}
  \begin{tabular}{lll}
      \item\label{fig:serial_sim}
      \aligntop{\includegraphics[width=0.24\linewidth]{serial.svg}}
      &
      \item\label{fig:binary_sim}
      \hspace{0.05\linewidth}\aligntop{\includegraphics[width=0.12\linewidth]{binary.svg}}
      &
      \item\label{fig:multistate_sim}
      \aligntop{\includegraphics[width=0.24\linewidth]{multistate.svg}}
      \\[1.3cm]
      \aligntop{\includegraphics[width=0.29\linewidth]{serial_fit_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.29\linewidth]{binary_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.29\linewidth]{multistate_lin_learnS.eps}}
      \\[3.5cm]
      \item\label{fig:pooled_sim}
      \aligntop{\includegraphics[width=0.29\linewidth]{pooled_deponly.svg}}
      &
      \item\label{fig:cascade_sim}
      \aligntop{\includegraphics[width=0.24\linewidth]{cascade.svg}}
      &
      \item\label{fig:nonuni_sim}
      \aligntop{\includegraphics[width=0.24\linewidth]{multistate_nonuni.svg}}
      \\[1.8cm]
      \aligntop{\includegraphics[width=0.29\linewidth]{pooled_deponly_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.29\linewidth]{cascade_fit_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.29\linewidth]{nonuni_fit_learnS.eps}}
  \end{tabular}

@@

    \cline{1-9}
    Serial   & 10 & $0.12$  & $0.14$  & $0.2$  & 0.5 & 0.89 & 0.11  & 100  \\%&\label{tr:serial_fit} \\
    Two-state     & 2  & $0.1$  & $0.1$  & $0.2$  & 0.5 & 0.6 & 0.4  & 5   \\%&\label{tr:binary} \\
    Multistate    & 10 & $0.3$  & $0.3$  & $0.4$  & 0.5 & 0.8 & 0.2  & 5   \\%&\label{tr:multistate_lin} \\
    Pooled res.\ & 7  & $0.008$        & $[0.0006,0.6]$  & $[0.001,1]$
                                          & 0.5 & 0.9 & 0.1 & 20 \\%&\label{tr:pooled_deponly}\\
    Cascade  & 14 & $0.386$  & $0.398$  & $0.466$  & 0.522 & 0.63 & 0.002  & 200  \\%&\label{tr:cascade_fit} \\
    Non-uni.\ & 12 & $0.4$    & $0.4$    & $0.53$   & 0.5 & 0.7 & 0.1 & 500  \\%&\label{tr:nonuni_fit} \\
    \cline{1-9}
  \end{tabular}}
  \end{myenuma}
  \caption[Simulation results for various models]{(\ref{fig:serial_sim}-\ref{fig:nonuni_sim}) Simulation results for various models, showing decrease in mean synaptic weight over time during gain increase training from the normal state (solid) and after gain-decrease pre-training (dashed) for wild-type (black) and \KO\ (red) models.
  (\ref{tab:params}) Parameters used for simulations.
  For the serial, two state and multistate models, the plasticity parameter listed is the transition probability between adjacent states.
  For the pooled resource model, the plasticity parameters are the minimum and maximum transition probability for the constituent two-state synapses.
  For the cascade and non-uniform multistate models, the plasticity parameter is the ratio of adjacent transition probabilities.}\label{fig:sim_results}
\end{figure}

@@

%\newcommand{\arrangefig}[1]{\begin{center}
% \begin{myenuma}
%  \item\aligntop{\includegraphics[width=7cm]{#1_learn.eps}}\label{fig:#1_learn}
%  \item\aligntop{\includegraphics[width=7cm]{#1_learnS.eps}}\label{fig:#1_learnS}
%  \\ \vp\vp
%  \item\label{fig:#1_eq}\begin{myenumi}
%                    \item\aligntop{\includegraphics[width=7cm]{#1_eq_WT.eps}}\label{fig:#1_eq_WT}
%                    \item\aligntop{\includegraphics[width=7cm]{#1_eq_KO.eps}}\label{fig:#1_eq_KO}
%                  \end{myenumi}
%  \\ \vp \vp
%  \item\label{fig:#1_pr}\begin{myenumi}
%                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_WT_nopre.eps}}\label{fig:#1_pr_WT_nopre}
%                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_WT_pre.eps}}\label{fig:#1_pr_WT_pre}
%                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_KO_nopre.eps}}\label{fig:#1_pr_KO_nopre}
%                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_KO_pre.eps}}\label{fig:#1_pr_KO_pre}
%                  \end{myenumi}
% \end{myenuma}
% \end{center}}
%
%\newcommand{\captiontext}[1]{ can be found in \autoref{tr:#1} of \autoref{tab:params}.
%  Time is measured in units of $1/r$, the mean time between plasticity events.
%  (\ref{fig:#1_learn}) Learning curves for wild-type and \KO\ models with and without pre-training.
%  (\ref{fig:#1_learnS}) Learning curves restricted to gain-increase training.
%  (\ref{fig:#1_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:#1_eq_WT}) wild-type and (\ref{fig:#1_eq_KO}) \KO\ models,
%  with states of weak synaptic strength to the left and strong states to the right.
%  (\ref{fig:#1_pr}) Evolution of probability distributions for (\ref{fig:#1_pr_WT_nopre},\ref{fig:#1_pr_WT_pre}) wild-type and  (\ref{fig:#1_pr_KO_nopre},\ref{fig:#1_pr_KO_pre}) \KO\ models without (\ref{fig:#1_pr_WT_nopre},\ref{fig:#1_pr_KO_nopre}) and with (\ref{fig:#1_pr_WT_pre},\ref{fig:#1_pr_KO_pre}) pre-training,
%  with states of weak synaptic strength at the top and strong states underneath. }
%
%\newcommand{\captionstart}[2]{Simulation results for the \textbf{#1} model with #2}
%\newcommand{\captionstarts}[2]{Simulation results for the #1 model with #2}
%\newcommand{\captionstartn}[1]{Simulation results for the \textbf{#1} model}
%\newcommand{\captionstartsn}[1]{Simulation results for the #1 model}
%
%\newcommand{\resultsfig}[4]{\begin{figure}
%  \arrangefig{#4}
%  \caption[\captionstarts{#1}{#2}]{\captionstart{#1}{#2 #3}.
%  Other parameters \captiontext{#4} } \label{fig:#4}
%\end{figure}}
%
%\newcommand{\resultsfign}[2]{\begin{figure}
%  \arrangefig{#2}
%  \caption[\captionstartsn{#1}]{\captionstartn{#1}.
%  Parameters \captiontext{#2} } \label{fig:#2}
%\end{figure}}

@@

The lack of monotonicity shown above allows this model to reproduce the key qualitative features of the experiments outlined in \autoref{sec:results}.
This can be illustrated by looking at a special case, where $q\pot = q\dep = q$ for the wild type, $f\dep_0 = \frac{1}{2}$, $f\dep\dec = \frac{1}{2} - \Delta f$ and $f\dep\inc = \frac{1}{2} - \Delta f$.

@@

With pre-training:
%
\begin{equation}\label{eq:multiKOpre}
\begin{aligned}
  \Phi &= 4{\Delta f}\, q \, \frac{(1-2\Delta f) - \beta(1+2\Delta f)}
          {(1-2\Delta f)^M - \beta^M(1+2\Delta f)^M}   \,
          \brk{\beta (1-2\Delta f) (1+2\Delta f)}^{M/2-1} \\
       &= 4{\Delta f}\, q\,\frac{(1-\beta)\beta^{M/2-1}}{1-\beta^M} + \CO(\Delta f)^2.
\end{aligned}
\end{equation}
%
Once again, we see that pre-training will speed up learning when $\Delta f$ is small, whereas, if $\Delta f$ is close to $-\half$, pre-training will initially slow down learning.

@@

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=0.45\linewidth]{multistate_betastar.eps}}\label{fig:multistate_betastar}
  \item\aligntop{\includegraphics[width=0.45\linewidth]{multistate_deltafstar.eps}}\label{fig:multistate_deltafstar}
 \end{myenuma}
 \end{center}
  \caption[The functions $\beta^*(M)$ and $\Delta f^*(\beta,M)$]{The functions (\ref{fig:multistate_betastar}) $\beta^*(M)$, which describes when the \KO\ models have impaired learning, and (\ref{fig:multistate_deltafstar}) $\Delta f^*(\beta,M)$ for $M=10$, which describes when pre-training enhances learning.}\label{fig:multistate_star}
\end{figure}

@@

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=0.4\linewidth]{pooled_deponly_scan.eps}
  \caption{Difference in initial learning rate in wild-type models, without and with gain-decrease pre-training.
  Learning, $L(t)$ is defined in \eqref{eq:learning}.
  Here, we show the maximum and minimum values of this quantity when scanning all 6 relevant parameters (see \protect\hyperlink{par:pooled_scan}{text}).
  We see that this quantity is always negative, whereas it was positive in the experiments.
  }\label{fig:pooled_scan}
\end{figure}

@@

% \begin{myenuma}

@@

% \end{myenuma}

@@

\begin{figure}
  \centering
  \begin{myenuma}
  \item\aligntop{\includegraphics[width=0.29\linewidth]{serial_longterm.eps}}\label{fig:serial_longterm}
  \item\aligntop{\includegraphics[width=0.29\linewidth]{binary_longterm.eps}}\label{fig:binary_longterm}
  \item\aligntop{\includegraphics[width=0.29\linewidth]{multistate_longterm.eps}}\label{fig:multistate_longterm} \\
  \item\aligntop{\includegraphics[width=0.29\linewidth]{pooled_longterm.eps}}\label{fig:pooled_longterm}
  \item\aligntop{\includegraphics[width=0.29\linewidth]{cascade_longterm.eps}}\label{fig:cascade_longterm}
  \item\aligntop{\includegraphics[width=0.29\linewidth]{nonuni_longterm.eps}}\label{fig:nonuni_longterm}
  \end{myenuma}
  \caption{ Simulation of training for long times after pre-training shows that it erases the effect of pre-training.
  These simulations were performed with the same parameters as in \autoref{fig:sim_results}\ref{tab:params}, but with much longer training times, for the (\ref{fig:serial_longterm}) serial, (\ref{fig:binary_longterm}) two-state, (\ref{fig:multistate_longterm}) multistate, (\ref{fig:pooled_longterm}) pooled resource, (\ref{fig:cascade_longterm} cascade and (\ref{fig:nonuni_longterm}) non-uniform multistate models.
  Compare with \autoref{fig:sim_results}.
  }\label{fig:longterm}
\end{figure}

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
\documentclass[10pt]{article}
%\usepackage[printfigures]{figcaps}
%\usepackage[nolists,nomarkers]{endfloat}
%Preamble:
\usepackage[inactive,tightpage]{preview}
\usepackage{a4wide}
\input{sl_preamble.tex}
\hypersetup{colorlinks,linkcolor=blue,citecolor=teal,urlcolor=teal}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figures/"}}
%
\usepackage{array}
%\newcounter{tablerow}[table]
%\newcommand{\tablerowautorefname}{row}
%\newenvironment{tabularn}[1]{\begin{tabular}{#1>{\refstepcounter{tablerow}}l}}{\end{tabular}}
%\usepackage{etoolbox}
%\AtBeginEnvironment{tabular}{\setcounter{tablerow}{0}}
\renewcommand{\figurename}{Appendix-figure}
\renewcommand{\figureautorefname}{Appendix-figure}
\DeclareCaptionLabelFormat{supp}{\textbf{#1 #2}}
\captionsetup{labelformat=supp}
\renewenvironment{myenumA}{\begin{inparaenum}[\bfseries A]}{\end{inparaenum}}
% ---------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\I}{\mathbf{I}}
%vec of ones
%equilibrium distribution
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%other symbols
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\frg}{\W^\mathrm{F}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
\newcommand{\norm}{_0}
\newcommand{\inc}{_{\text{inc}}}
\newcommand{\dec}{_{\text{dec}}}
\newcommand{\incdec}{_{\text{inc/dec}}}
\newcommand{\wt}{_{\text{WT}}}
\newcommand{\ko}{_{\text{K$^\mathrm{b}$D$^\mathrm{b}$-/-}}}
\newcommand{\KO}{K$^\mathrm{b}$D$^{\mathrm{b}-/-}$}
%\newcommand{\ko}{_{\text{MHC}}}
%\newcommand{\KO}{MHC}
\newcommand{\tpre}{t_{\text{pre}}}
\newcommand{\ttrain}{t_{\text{train}}}
%\newcommand{\lmax}{_{\text{max}}}
%\newcommand{\lmin}{_{\text{min}}}
\newcommand{\modelfig}[1][A]{Figure 4#1 of the main text}
\newcommand{\datafig}[1][B]{Figure 3#1 of the main text}
\newcommand{\chrfig}[1][B]{Figure 2#1 of the main text}
\newcommand{\compfig}[1][A]{Figure 2 -- figure supplement 2#1}
\newcommand{\basefig}{Figure 1 -- figure supplement 2}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Appendix to ``Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis''}
%
%% Author List:
%%
%\author{An Author$^a$, Another Author$^b$ and Yet Another Author$^c$\\
%%
%\small{\emph{$^a$ Address 1}}\\
%\small{\emph{$^b$ Address 2}}\\
%\small{\emph{$^c$ Address 3}}\\
%}
\author{}
\date{}

@@

\begin{figure}
\begin{preview}
 \begin{center}
   \begin{myenumA}
  \begin{tabular}{l@{\hspace{0.05\linewidth}}l}
    \item\aligntop{\includegraphics[height=1.7cm]{serial.svg}}\label{fig:serial_model}&
    \item\aligntop{\includegraphics[height=1.7cm]{binary.svg}}\label{fig:binary_model}\\[1.7cm]
    \item\aligntop{\includegraphics[height=1.7cm]{multistate.svg}}\label{fig:multistate_model}&
    \item\aligntop{\includegraphics[height=2.5cm]{cascade.svg}}\label{fig:cascade_model}\\[2.5cm]
    \item\aligntop{\includegraphics[height=2.3cm]{pooled_deponly.svg}}\label{fig:pooled_model}&
    \item\aligntop{\includegraphics[height=2.3cm]{multistate_nonuni.svg}}\label{fig:nonuni_model}
  \end{tabular}
   \end{myenumA}
 \end{center}
\end{preview}
  \caption[Transition probabilities for different models]{{Transition probabilities for different models.}
  Potentiation induces transitions indicated by orange arrows, depression indicated by blue arrows.
  States of strong/weak synaptic weight indicated by orange/blue circles.
  (\ref{fig:serial_model}) In the serial model the transition probabilities for potentiation/depression are all equal and it is parameterised by these two values.
  The synaptic weight takes only two values, $\pm1$.
  (\ref{fig:binary_model}) The two-state model is parameterised by the two transition probabilities.
  (\ref{fig:multistate_model}) In the multistate model the transition probabilities for potentiation/depression are all equal and it is parameterised  by these two values.
  The synaptic weight varies linearly in the interval $[-1,1]$.
  (\ref{fig:cascade_model}) In the cascade model, the transition probabilities decay geometrically with a parameter $x$ (see \cite{Fusi2005cascade}) and synaptic weight takes only two values.
  (\ref{fig:pooled_model}) In the pooled resource model,
  Several two-state synapses share resources that are required for potentiation and depression.
  These resources are depleted as more synapses are potentiated or depressed.
  This pool of synapses can be modelled as one compound synapse.
  (\ref{fig:nonuni_model}) In the non-uniform multistate model
  the synaptic weight varies linearly in the interval $[-1,1]$, similar to the multistate model, but the transition probabilities between adjacent states decays exponentially away from the central transition for both potentiation and depression.
  } \label{fig:models}
\end{figure}

@@

\begin{figure}[p]
\begin{preview}
\begin{myenumA}
  \begin{tabular}{lll}
      \item\label{fig:serial_sim}
      \aligntop{\includegraphics[width=0.24\linewidth]{serial.svg}}
      &
      \item\label{fig:binary_sim}
      \hspace{0.05\linewidth}\aligntop{\includegraphics[width=0.12\linewidth]{binary.svg}}
      &
      \item\label{fig:multistate_sim}
      \aligntop{\includegraphics[width=0.24\linewidth]{multistate.svg}}
      \\[1.3cm]
      \aligntop{\includegraphics[width=0.29\linewidth]{serial_fit_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.29\linewidth]{binary_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.29\linewidth]{multistate_lin_learnS.eps}}
      \\[3.5cm]
      \item\label{fig:pooled_sim}
      \aligntop{\includegraphics[width=0.29\linewidth]{pooled_deponly.svg}}
      &
      \item\label{fig:cascade_sim}
      \aligntop{\includegraphics[width=0.24\linewidth]{cascade.svg}}
      &
      \item\label{fig:nonuni_sim}
      \aligntop{\includegraphics[width=0.24\linewidth]{multistate_nonuni.svg}}
      \\[1.8cm]
      \aligntop{\includegraphics[width=0.29\linewidth]{pooled_deponly_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.29\linewidth]{cascade_fit_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.29\linewidth]{nonuni_fit_learnS.eps}}
  \end{tabular}

@@

    \cline{1-9}
    Serial   & 10 & $0.12$  & $0.14$  & $0.2$  & 0.5 & 0.89 & 0.11  & 100  \\%&\label{tr:serial_fit} \\
    Two-state     & 2  & $0.1$  & $0.1$  & $0.2$  & 0.5 & 0.6 & 0.4  & 5   \\%&\label{tr:binary} \\
    Multistate    & 10 & $0.3$  & $0.3$  & $0.4$  & 0.5 & 0.8 & 0.2  & 5   \\%&\label{tr:multistate_lin} \\
    Pooled res.\ & 7  & $0.008$        & $[0.0006,0.6]$  & $[0.001,1]$
                                          & 0.5 & 0.9 & 0.1 & 20 \\%&\label{tr:pooled_deponly}\\
    Cascade  & 14 & $0.386$  & $0.398$  & $0.466$  & 0.522 & 0.63 & 0.002  & 200  \\%&\label{tr:cascade_fit} \\
    Non-uni.\ & 12 & $0.4$    & $0.4$    & $0.53$   & 0.5 & 0.7 & 0.1 & 500  \\%&\label{tr:nonuni_fit} \\
    \cline{1-9}
  \end{tabular}}
  \end{myenumA}
\end{preview}
  \caption[Simulation results for various models]{(\ref{fig:serial_sim}-\ref{fig:nonuni_sim}) Simulation results for various models, showing decrease in mean synaptic weight over time during gain increase training from the normal state (solid) and after gain-decrease pre-training (dashed) for wild-type (black) and \KO\ (red) models.
  (\ref{tab:params}) Parameters used for simulations.
  For the serial, two state and multistate models, the plasticity parameter listed is the transition probability between adjacent states.
  For the pooled resource model, the plasticity parameters are the minimum and maximum transition probability for the constituent two-state synapses.
  For the cascade and non-uniform multistate models, the plasticity parameter is the ratio of adjacent transition probabilities.}\label{fig:sim_results}
\end{figure}

@@

%\newcommand{\arrangefig}[1]{\begin{center}
% \begin{myenumA}
%  \item\aligntop{\includegraphics[width=7cm]{#1_learn.eps}}\label{fig:#1_learn}
%  \item\aligntop{\includegraphics[width=7cm]{#1_learnS.eps}}\label{fig:#1_learnS}
%  \\ \vp\vp
%  \item\label{fig:#1_eq}\begin{myenumi}
%                    \item\aligntop{\includegraphics[width=7cm]{#1_eq_WT.eps}}\label{fig:#1_eq_WT}
%                    \item\aligntop{\includegraphics[width=7cm]{#1_eq_KO.eps}}\label{fig:#1_eq_KO}
%                  \end{myenumi}
%  \\ \vp \vp
%  \item\label{fig:#1_pr}\begin{myenumi}
%                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_WT_nopre.eps}}\label{fig:#1_pr_WT_nopre}
%                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_WT_pre.eps}}\label{fig:#1_pr_WT_pre}
%                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_KO_nopre.eps}}\label{fig:#1_pr_KO_nopre}
%                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_KO_pre.eps}}\label{fig:#1_pr_KO_pre}
%                  \end{myenumi}
% \end{myenumA}
% \end{center}}
%
%\newcommand{\captiontext}[1]{ can be found in \autoref{tr:#1} of \autoref{tab:params}.
%  Time is measured in units of $1/r$, the mean time between plasticity events.
%  (\ref{fig:#1_learn}) Learning curves for wild-type and \KO\ models with and without pre-training.
%  (\ref{fig:#1_learnS}) Learning curves restricted to gain-increase training.
%  (\ref{fig:#1_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:#1_eq_WT}) wild-type and (\ref{fig:#1_eq_KO}) \KO\ models,
%  with states of weak synaptic strength to the left and strong states to the right.
%  (\ref{fig:#1_pr}) Evolution of probability distributions for (\ref{fig:#1_pr_WT_nopre},\ref{fig:#1_pr_WT_pre}) wild-type and  (\ref{fig:#1_pr_KO_nopre},\ref{fig:#1_pr_KO_pre}) \KO\ models without (\ref{fig:#1_pr_WT_nopre},\ref{fig:#1_pr_KO_nopre}) and with (\ref{fig:#1_pr_WT_pre},\ref{fig:#1_pr_KO_pre}) pre-training,
%  with states of weak synaptic strength at the top and strong states underneath. }
%
%\newcommand{\captionstart}[2]{Simulation results for the \textbf{#1} model with #2}
%\newcommand{\captionstarts}[2]{Simulation results for the #1 model with #2}
%\newcommand{\captionstartn}[1]{Simulation results for the \textbf{#1} model}
%\newcommand{\captionstartsn}[1]{Simulation results for the #1 model}
%
%\newcommand{\resultsfig}[4]{\begin{figure}
%  \arrangefig{#4}
%  \caption[\captionstarts{#1}{#2}]{\captionstart{#1}{#2 #3}.
%  Other parameters \captiontext{#4} } \label{fig:#4}
%\end{figure}}
%
%\newcommand{\resultsfign}[2]{\begin{figure}
%  \arrangefig{#2}
%  \caption[\captionstartsn{#1}]{\captionstartn{#1}.
%  Parameters \captiontext{#2} } \label{fig:#2}
%\end{figure}}

@@

The lack of monotonicity shown above allows this model to reproduce the key qualitative features of the experiments outlined in \autoref{sec:results}.
This can be illustrated by looking at a special case, where $q\pot = q\dep = q$ for the wild type, $f\dep_0 = \frac{1}{2}$, $f\dep\dec = \frac{1}{2} - \Delta f$ and $f\dep\inc = \frac{1}{2} + \Delta f$.

@@

With pre-training:
%
\begin{equation}\label{eq:multiKOpre}
\begin{aligned}
  \Phi &= 4{\Delta f}\, q \, \frac{(1-2\Delta f) - \beta(1+2\Delta f)}
          {(1-2\Delta f)^M - \beta^M(1+2\Delta f)^M}   \,
          \brk{\beta (1-2\Delta f) (1+2\Delta f)}^{M/2-1} \\
       &= 4{\Delta f}\, q\,\frac{(1-\beta)\beta^{M/2-1}}{1-\beta^M} + \CO(\Delta f)^2.
\end{aligned}
\end{equation}
%
Once again, we see that pre-training will speed up learning when $\Delta f$ is small, whereas, if $\Delta f$ is close to $\half$, pre-training will initially slow down learning.

@@

\begin{figure}
\begin{preview}
 \begin{center}
 \begin{myenumA}
  \item\aligntop{\includegraphics[width=0.45\linewidth]{multistate_betastar.eps}}\label{fig:multistate_betastar}
  \item\aligntop{\includegraphics[width=0.45\linewidth]{multistate_deltafstar.eps}}\label{fig:multistate_deltafstar}
 \end{myenumA}
 \end{center}
\end{preview}
  \caption[The functions $\beta^*(M)$ and $\Delta f^*(\beta,M)$]{The functions
  (\ref{fig:multistate_betastar}) $\beta^*(M)$, which describes when the \KO\ models have impaired learning,
  and (\ref{fig:multistate_deltafstar}) $\Delta f^*(\beta,M)$ for $M=10$, which describes when pre-training enhances learning.}\label{fig:multistate_star}
\end{figure}

@@

\begin{figure}
\begin{preview}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=0.4\linewidth]{pooled_deponly_scan.eps}
\end{preview}
  \caption{Difference in initial learning rate in wild-type models, without and with gain-decrease pre-training.
  Learning, $L(t)$ is defined in \eqref{eq:learning}.
  Here, we show the maximum and minimum values of this quantity when scanning all 6 relevant parameters (see \protect\hyperlink{par:pooled_scan}{text}).
  We see that this quantity is always negative, whereas it was positive in the experiments.
  }\label{fig:pooled_scan}
\end{figure}

@@

% \begin{myenumA}

@@

% \end{myenumA}

@@

\begin{figure}
\begin{preview}
  \centering
  \begin{myenumA}
  \item\aligntop{\includegraphics[width=0.29\linewidth]{serial_longterm.eps}}\label{fig:serial_longterm}
  \item\aligntop{\includegraphics[width=0.29\linewidth]{binary_longterm.eps}}\label{fig:binary_longterm}
  \item\aligntop{\includegraphics[width=0.29\linewidth]{multistate_longterm.eps}}\label{fig:multistate_longterm} \\
  \item\aligntop{\includegraphics[width=0.29\linewidth]{pooled_longterm.eps}}\label{fig:pooled_longterm}
  \item\aligntop{\includegraphics[width=0.29\linewidth]{cascade_longterm.eps}}\label{fig:cascade_longterm}
  \item\aligntop{\includegraphics[width=0.29\linewidth]{nonuni_longterm.eps}}\label{fig:nonuni_longterm}
  \end{myenumA}
\end{preview}
  \caption{ Simulation of training for long times after pre-training shows that it erases the effect of pre-training.
  These simulations were performed with the same parameters as in \autoref{fig:sim_results}\ref{tab:params}, but with much longer training times, for the (\ref{fig:serial_longterm}) serial, (\ref{fig:binary_longterm}) two-state, (\ref{fig:multistate_longterm}) multistate, (\ref{fig:pooled_longterm}) pooled resource, (\ref{fig:cascade_longterm} cascade and (\ref{fig:nonuni_longterm}) non-uniform multistate models.
  Compare with \autoref{fig:sim_results}.
  }\label{fig:longterm}
\end{figure}
